---
title: "Visualizations"
---

```{r}
#| include: false
library(tabviz)
library(dplyr)
```

tabviz supports embedded visualizations within table columns. This section covers the visualization column types and their common features.

## Visualization Column Types

| Column | Purpose | Guide |
|--------|---------|-------|
| `col_forest()` | Forest plots with confidence intervals | [Forest Plots](forest-plots.qmd) |
| `col_bar()` | Horizontal bars | [Columns](../columns.qmd#visualizations) |
| `col_sparkline()` | Mini line/area/bar charts | [Columns](../columns.qmd#visualizations) |

## Common Features

All visualization columns share these capabilities:

- **Axis configuration** — Range, ticks, gridlines
- **Interactivity** — Hover, tooltips, zoom
- **Theming** — Colors adapt to the active theme
- **Export** — SVG, PNG, PDF output

---

## Interactivity

::: {.callout-note}
## Interactive by Default

All tabviz widgets include these interactions out of the box:

- **Hover highlighting** on rows
- **Click to select** rows
- **Column sorting** via header clicks
- **Column resizing** via drag
- **Group collapsing** via chevron clicks
- **Download button** on hover (top-right)
:::

### Hover Tooltips

Tooltips are **opt-in**. Specify fields to show when hovering over markers:

```{r}
data(glp1_trials)

glp1_trials |>
  filter(row_type == "data", group == "Main Trials") |>
  head(4) |>
  tabviz(label = "study",
    interaction = web_interaction(tooltip_fields = c("n", "events", "pvalue")),
    footnote = "Hover over markers to see tooltip",
    columns = list(
      col_forest(point = "hr", lower = "lower", upper = "upper",
                 scale = "log", null_value = 1)
    )
  )
```

### Interaction Controls

```r
web_interaction(

  tooltip_fields = NULL,    # Column names for tooltip
  enable_sort = TRUE,       # Click headers to sort
  enable_collapse = TRUE,   # Click group headers to collapse
  enable_select = TRUE,     # Click rows to select
  enable_hover = TRUE,      # Highlight on hover
  enable_resize = TRUE,     # Drag column borders
  enable_export = TRUE,     # Download button
  enable_themes = "default" # Theme selection menu
)
```

### Interaction Presets

| Preset | Description |
|--------|-------------|
| `web_interaction()` | Full interactivity (default) |
| `web_interaction_minimal()` | Hover only—no sorting/selection |
| `web_interaction_publication()` | Fully static (for print) |

```{r}
#| eval: false
# Publication-ready static output
tabviz(data, label = "study",
  interaction = web_interaction_publication(),
  columns = list(col_forest(...))
)
```

---

## Zoom & Sizing

Control how visualizations fit within their container:

| Argument | Options | Description |
|----------|---------|-------------|
| `zoom` | 0.5 to 2.0 | Initial zoom level (default 1.0) |
| `auto_fit` | TRUE/FALSE | Shrink to fit container if too large (default TRUE) |
| `max_width` | pixels or NULL | Maximum container width |
| `max_height` | pixels or NULL | Maximum container height (enables scrolling) |

```{r}
#| eval: false
# Constrain to specific dimensions
tabviz(data, label = "study",
  max_width = 800,
  max_height = 400,
  columns = list(...)
)
```

---

## Exporting Visualizations

tabviz supports exporting to SVG, PNG, and PDF.

### Using save_plot()

```r
# Create a visualization
p <- tabviz(data, label = "study", columns = list(
  col_forest(point = "hr", lower = "lower", upper = "upper",
             scale = "log", null_value = 1)
))

# Save as SVG (vector)
save_plot(p, "figure.svg")

# Save as PNG (raster, high-res)
save_plot(p, "figure.png", width = 1200, scale = 2)

# Save as PDF
save_plot(p, "figure.pdf", width = 800)
```

### Output Formats

| Format | Extension | Use Case | Dependencies |
|--------|-----------|----------|--------------|
| SVG | `.svg` | Vector graphics, web, editing | None |
| PNG | `.png` | Documents, slides | `rsvg` package |
| PDF | `.pdf` | Print, publications | `rsvg` package |

### Browser Export

Interactive plots include a download button (visible on hover in top-right):

1. Hover over plot to reveal button
2. Click to open format menu
3. Choose SVG or PNG

---

## See Also

- [Forest Plots](forest-plots.qmd) — Detailed `col_forest()` guide
- [Columns](../columns.qmd) — All column types including `col_bar()` and `col_sparkline()`
- [Export](../export.qmd) — Advanced export options
- [Shiny Integration](../shiny.qmd) — Interactive applications
