---
title: "webforest"
subtitle: "Interactive Forest Plots for R"
---

```{r}
#| include: false
library(webforest)
```

## Overview

**webforest** is an R htmlwidgets package for creating interactive, web-native forest plots. While traditionally used for meta-analysis, it supports any data with point estimates and confidence intervals.

```{r}
#| echo: false
meta_data <- data.frame(
  study = c("Smith 2020", "Jones 2021", "Lee 2022", "Chen 2023", "Park 2024"),
  hr = c(0.72, 0.85, 0.91, 0.68, 0.79),
  lower = c(0.55, 0.70, 0.75, 0.52, 0.61),
  upper = c(0.95, 1.03, 1.10, 0.89, 1.02),
  n = c(245, 180, 320, 156, 210)
)

forest_plot(meta_data,
  point = "hr", lower = "lower", upper = "upper",
  label = "study", null_value = 1, scale = "log",
  columns = list(col_numeric("n", "N", position = "left")),
  axis_label = "Hazard Ratio (95% CI)",
  theme = web_theme_modern()
)
```

## Features

- **Modern web rendering** using Svelte 5 and D3.js
- **Multiple preset themes** (JAMA, Lancet, presentation, dark mode)
- **Flexible column system** with special renderers (bars, p-values, sparklines)
- **Hierarchical grouping** with collapsible sections
- **Interactive features** (hover tooltips, row selection)
- **Static export** to SVG, PNG, and PDF
- **Fluent API** for theme customization

## Installation

```r
# install.packages("pak")
pak::pak("kaskarn/webforest")
```

## Quick Example

```r
library(webforest)

forest_plot(data,
  point = "estimate",
  lower = "ci_lower",
  upper = "ci_upper",
  label = "study",
  null_value = 1,
  scale = "log"
)
```

## Guide

Learn how to use webforest:

| Chapter | Description |
|---------|-------------|
| [Quick Start](guide/quick-start.qmd) | Installation and basic usage |
| [Themes](guide/themes.qmd) | Preset themes and customization |
| [Columns](guide/columns.qmd) | Data columns and special formatting |
| [Grouping & Rows](guide/grouping-rows.qmd) | Hierarchical data and row styling |
| [Exporting](guide/exporting.qmd) | Save plots as SVG, PNG, or PDF |
| [Axis & Annotations](guide/axis-annotations.qmd) | Axis control and reference lines |

## More Resources

- [Cookbook](cookbook.qmd) - Common tasks and patterns
- [Gallery](gallery.qmd) - Interactive examples
- [Reference](reference.qmd) - API documentation
